\EVOSUITE at the SBST 2020 Tool Competition

### 2020-04-04 papers/sbst20/main.tex
Add text

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
TBD
\end{abstract}

@@

@@

@@

@@

\bibliographystyle{ACM-Reference-Format}
\bibliography{papers}

>>>>

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
%
  \EVOSUITE is a search-based tool that automatically generates
  executable unit tests for Java code (JUnit tests).  This paper
  summarizes the results and experiences of \EVOSUITE's participation
  at the eighth unit testing competition at SBST 2020, where \EVOSUITE
  achieved the highest overall score (\TOTALPOINTS points) for the
  seventh time in eight editions of the competition.
  %
\end{abstract}

@@

Automated unit test generation can support developers and testers, produce
regression test suites, and is an enabler for dynamic program analyses. The
annual unit test generation aims to foster research and development of
automated unit test generators. This paper describes the results obtained by
the \EVOSUITE test generation tool~\cite{FrA11c} in this competition. \EVOSUITE
uses meta-heuristic search in order to evolve unit test suites with high
coverage, and automatically produces regression oracles in the form of test
assertions. In the 8th instance of the competition at the International
Workshop on Search-Based Software Testing (SBST) 2020, \EVOSUITE achieved an
overall score of \TOTALPOINTS, which was the highest among the competing and
baseline tools. This paper describes the results obtained by the \EVOSUITE test
generation tool in this competition.

@@

\EVOSUITE~\cite{FrA11c} is a search-based unit test generation
tool~\cite{GoA_TSE12}. Table~\ref{tool-description} summarizes the features of
\EVOSUITE in the standard format of the SBST unit testing competition: Given
just the Java classpath containing all compiled dependencies and the name of a
class under test, \EVOSUITE automatically generates a set of JUnit test cases
aimed at maximinizing code coverage. \EVOSUITE can be used on the command line,
as a Maven plugin, or using plugins for the Eclipse and IntelliJ development
environments~\cite{ICST16_Tool}.

Over the course of its development, several different search algorithms have
been evaluated, starting with a basic genetic algorithm. \EVOSUITE's encoding of test cases for the evolutionary search (i.e., its chromosomes) consists of variable-length sequences of Java statements (e.g., primitive statements and calls on the class under test). The usual search operators used in evolutionary search (e.g., selection, crossover, mutation) are adapted for this particular representation. 
%
In the original approach, individuals of the genetic algorithm were whole test
suites, with the optimization goal of finding a test suite that maximizes code
coverage. This was later improved by adding an archive of
solutions~\cite{emse_archive} to keep the search focused on uncovered goals,
iteratively discarding covered goals and storing the tests that covered them.

Recently, the \textit{Dynamic Many-Objective Sorting Algorithm} (DynaMOSA) search algorithm~\cite{dynamosa, panichella:ssbse2018}  has been shown to be the most effective approach of all the algorithms evaluated so far. DynaMOSA is a many-objective algorithm, where individuals of the search population are test cases, rather than test suites, and the optimization is driven by a collection of individual fitness functions, one for each coverage objective (e.g., line or branch).

The fitness functions in \EVOSUITE are based on traditional heuristics for code
coverage, such as the branch distance and the approach level
(see~\cite{GoA_TSE12} for more details).
%
\EVOSUITE supports multiple different coverage criteria, which can be optimized
for at the same time. The default configuration combines branch coverage with
mutation testing~\cite{emse14_mutation} and other basic
criteria~\cite{rojas2015combining}.
%
In order to cope with the potentially large number of coverage objectives,
DynaMOSA prioritizes them during the search according to their structural
dependencies in the control dependency graph. Initially the search focuses on
coverage objectives positioned higher in the hierarchy, and the remaining
objectives are incrementally inserted in later generations when their dominator
requirements are covered.

After the search has used up the available search budget (or alternatively, has
achieved 100\% coverage of all coverage objectives), \EVOSUITE applies various
post-search optimizations aimed to improve the readability of the generated
tests~\cite{FrA11c,FrA13a}, such as minimization and addition of test assertions using mutation
analysis~\cite{10.1109/TSE.2011.93}. It also checks all generated tests for compile errors (which may be the result of bugs in \EVOSUITE) or flakiness caused by non-determinism in the class under test, not covered by \EVOSUITE's extensive instrumentation.

\EVOSUITE has been evaluated on open
source as well as industrial software in terms of code
coverage~\cite{fraser2014large,emse_archive,ea_evaluation,dynamosa},
fault finding
effectiveness~\cite{shamshiri2015automatically,moein2017}, and effects
on developer productivity~\cite{TOSEM_userstudy,ISSTA15_Study} and
software maintenance~\cite{ICST2018_Maintenance}.
%
\EVOSUITE has a longstanding record of success at the unit testing tool
competition, having ranked second in the third edition of the
competition~\cite{evosuiteAtSbst2015} and first in all the other
editions~\cite{evosuiteAtSbst2013,evosuiteAtFittest2013,evosuiteAtSbst2016,evosuiteAtSbst2017,evosuiteAtSbst2018}. In the 2019 SBST contest, \EVOSUITE
achieved the highest overall score of all participating tools~\cite{evosuiteAtSbst2019}, although the
performance was inhibited by some bugs.

@@

Similar to the previous years, the configuration of \EVOSUITE for the 2020
competition is largely based on its default values since these have been tuned
extensively~\cite{arcuri2013parameter}. 
%
The search algorithm used was DynaMOSA~\cite{dynamosa}, optimizing for the
default set of coverage criteria~\cite{rojas2015combining} (i.e., line
coverage, branch coverage, branch coverage by direct method invocations, weak
mutation testing, output coverage, exception coverage).
%
Other features enabled by default include the use of frequency-based weighted
constants for seeding~\cite{sakti2015instance} as well as support for Java
Enterprise Edition features~\cite{arcuri2016java}. In the case of difficult dependencies and branches that cannot be covered, \EVOSUITE can start using mock objectes once a certain percentage of the search
budget has passed~\cite{ICST_Mocking17} .

No major new features have been introduced in \EVOSUITE since the 2019 competition, but several bugs that affected \EVOSUITE's performance during the previous competition have been fixed. In particular, there were several problematic cases when \EVOSUITE was run using very small search budgets.

The test minimization step used by \EVOSUITE is computationally expensive and
sometimes omitted for empirical studies; in the competition we always enable
the post-processing step of test minimization, because minimized tests are less
likely to break or expose flakiness. However, we aimed to reduce the
post-processing time by including all regression assertions rather than
filtering them with mutation analysis~\cite{10.1109/TSE.2011.93}. While this
makes test cases less readable and potentially more brittle with respect to
future changes in the software under test, neither of these aspects is
evaluated as part of the SBST contest.

\EVOSUITE uses different phases (e.g., initialisation, search, minimization,
assertion generation, compilation check, removal of flaky tests). Like in
previous competitions (e.g.,~\cite{evosuiteAtSbst2016}) we allocated 50\% of
the overall time set by the competition organisers for the search, and
distributed the other 50\% equally to the remaining phases.

@@

\balance
\bibliographystyle{ACM-Reference-Format}
\bibliography{papers}
